### 2023-09-29 chapters/discussion.tex
Updates

\section{\Cref{chp:paper-retrospective} revisited: Uncertainty}
The work in \textcite{wenstrup_retrospective_2023} deals with predictive performance and analyses feature importance but does not explicitly consider uncertainty estimation.

\begin{figure}
    \begin{subfigure}[c]{0.48\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{python_plotting/calibration_curve_ensemble_and_all_models_uncalibrated.pdf}
        \caption{}
        \label{fig_discussion:calibration_curve_ensemble_and_all_models_uncalibrated}
    \end{subfigure}
    % \hfill
    \begin{subfigure}[c]{0.48\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{python_plotting/histogram_ensemble_and_single_model.pdf}
        \caption{}
        \label{fig_hierarchical:histogram_ensemble_and_single_model}
    \end{subfigure}
\end{figure}

>>>>

\section{\Cref{chp:paper-retrospective} revisited: Uncertainty}
The work in \textcite{wenstrup_retrospective_2023} focuses on predictive performance and an analysis of feature importance but does not explicitly consider uncertainty estimation. To

\begin{figure}
    \begin{subfigure}[c]{0.48\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{python_plotting/calibration_curve_ensemble_and_all_models_uncalibrated.pdf}
        % \caption{}
        % \label{fig_discussion:calibration_curve_ensemble_and_all_models_uncalibrated}
    \end{subfigure}
    % \hfill
    \begin{subfigure}[c]{0.48\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{python_plotting/histogram_ensemble_and_single_model.pdf}
        % \caption{}
        % \label{fig_discussion:histogram_ensemble_and_single_model}
    \end{subfigure}
    \caption[Calibration curve for the uncalibrated stroke recognition model and empirical distribution of predicted probabilities.]{\subref{fig_discussion:calibration_curve_ensemble_and_all_models_uncalibrated} \Cref{fig_discussion:calibration_curve_ensemble_and_all_models_uncalibrated} shows the calibration curve for the uncalibrated ensemble model with median F1-score also reported in \cref{tab_retrospective:table3-occlusion-analysis} and \cref{fig_retrospective:figure1-roc-curve}. \subref{fig_discussion:histogram_ensemble_and_single_model} Histogram of predicted probabilities.}
\end{figure}

% \subsectionP{Ensembling technique}
% To form an ensemble from several models, we need a method to form a single prediction from the outputs of the individual models.
% To allow us to evaluate an impact score for each word feature in our ablation study, we wanted our ensemble to provide not only predictions but also associated probability scores on a continuous scale. A majority voting scheme would only provide as many different scores as models, in our case five, which is arguably too coarse a resolution.

### 2023-09-29 chapters/introduction.tex
Updates

\section{Thesis scope and outline}
%
% OUTLINE: 
% - Tie together the different topics of the thesis and point briefly to the relevant papers.
%
% The complete set of research published as part of this project covers a number of topics related to decision-support in medical conversations. 
% One group of the primary papers is concerned with generative latent variable models and their applications to estimation of epistemic uncertainty and speech modelling \cite{havtorn_hierarchical_2021,havtorn_benchmarking_2022,bergamin_modelagnostic_2022}. 
% Another group of studies examines self-supervised speech representation learning as an alternative to generative latent variable models \cite{mohamed_selfsupervised_2022,borgholt_brief_2022} and explores them for speech recognition \cite{borgholt_scaling_2021} and spoken language understanding \cite{borgholt_we_2021}. 
% Finally, a group deals with applications of machine learning within the medical domain, including recognition of stroke cases in calls to medical helplines \cite{wenstrup_retrospective_2023} and medical coding of clinical notes \cite{edin_automated_2023}. 
%
This introduction provided a high-level overview of the motivation behind the research project by focusing on the use-cases of stroke recognition and automated medical coding as well as speech processing and the importance of uncertainty quantification. 
The remainder of \cref{part:background} consists of two chapters. \Cref{chp:technical-background} provides relevant technical background to the papers of the thesis, including uncertainty, out-of-distribution detection, and variational autoencoders while \cref{chp:main-contributions} outlines the main contributions of the thesis in relation to the published papers and the research project as a whole.

>>>>

\section{Research hypotheses}

\todo[inline]{Formulate research hypotheses}

\section{Thesis scope and outline}
%
% OUTLINE: 
% - Tie together the different topics of the thesis and point briefly to the relevant papers.
%
% The complete set of research published as part of this project covers a number of topics related to decision-support in medical conversations. 
% One group of the primary papers is concerned with generative latent variable models and their applications to estimation of epistemic uncertainty and speech modelling \cite{havtorn_hierarchical_2021,havtorn_benchmarking_2022,bergamin_modelagnostic_2022}. 
% Another group of studies examines self-supervised speech representation learning as an alternative to generative latent variable models \cite{mohamed_selfsupervised_2022,borgholt_brief_2022} and explores them for speech recognition \cite{borgholt_scaling_2021} and spoken language understanding \cite{borgholt_we_2021}. 
% Finally, a group deals with applications of machine learning within the medical domain, including recognition of stroke cases in calls to medical helplines \cite{wenstrup_retrospective_2023} and medical coding of clinical notes \cite{edin_automated_2023}. 
%
This introduction provided a high-level overview of the motivation behind the research project by focusing on the use-cases of stroke recognition and automated medical coding as well as speech processing and the importance of uncertainty quantification. 
The remainder of \cref{part:background} consists of two chapters. \Cref{chp:technical-background} provides relevant technical background to the papers of the thesis, including uncertainty, out-of-distribution detection, and variational autoencoders while \cref{chp:main-contributions} outlines the main contributions of the thesis via the published papers in relation to the research hypotheses.

### 2023-09-29 chapters/paper_automated.tex
Updates

\begin{figure}[t]
    \centering
    \begin{subfigure}[b]{0.8\textwidth}
        \centering
        \includegraphics[width=\linewidth]{paper_automated/threshold_tuning_micro_full.png}
        % \caption{}
        % \label{fig:threshold_tuning_micro}
    \end{subfigure}
    \begin{subfigure}[b]{0.8\textwidth}
        \centering
        \includegraphics[width=\linewidth]{paper_automated/threshold_tuning_macro_full.png}
        % \caption{}
        % \label{fig:threshold_tuning_macro}
    \end{subfigure}%
    \caption[The relationship between chosen threshold and F1 score of every reproduced model in \cref{tab:reproduced_results}]{The relationship between chosen threshold and F1 score of every reproduced model in \cref{tab:reproduced_results}. The left figure shows the micro F1 score, and the right shows the macro F1 score. The models were evaluated on MIMIC-III \textit{clean}.}
    \label{fig:threshold_tuning}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \begin{subfigure}[b]{0.8\textwidth}
        \centering
        \includegraphics[width=\linewidth]{paper_automated/train_size_f1_micro.png}
        % \caption{}
        % \label{fig:train_size_micro}
    \end{subfigure}
    \begin{subfigure}[b]{0.8\textwidth}
        \centering
        \includegraphics[width=\linewidth]{paper_automated/train_size_f1_macro.png}
        % \caption{}
        % \label{fig:train_size_macro}
    \end{subfigure}
    \caption[The relationship between the number of training examples and F1 score on MIMIC-IV \textit{ICD-9}]{The relationship between the number of training examples and F1 score on MIMIC-IV \textit{ICD-9}. The left figure shows the F1 Micro score on the y-axis, while the right figure shows the F1 Macro score.}
    \label{fig:train_size}
\end{figure}

>>>>

\begin{figure}[t]
    \centering
    \begin{subfigure}[b]{0.6\textheight}
        \centering
        \includegraphics[width=\textwidth]{paper_automated/threshold_tuning_micro_full.png}
        % \caption{}
        % \label{fig:threshold_tuning_micro}
    \end{subfigure}
    \begin{subfigure}[b]{0.6\textheight}
        \centering
        \includegraphics[width=\textwidth]{paper_automated/threshold_tuning_macro_full.png}
        % \caption{}
        % \label{fig:threshold_tuning_macro}
    \end{subfigure}%
    \caption[The relationship between chosen threshold and F1 score of every reproduced model in \cref{tab:reproduced_results}]{The relationship between chosen threshold and F1 score of every reproduced model in \cref{tab:reproduced_results}. The left figure shows the micro F1 score, and the right shows the macro F1 score. The models were evaluated on MIMIC-III \textit{clean}.}
    \label{fig:threshold_tuning}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \begin{subfigure}[b]{0.6\textheight}
        \centering
        \includegraphics[width=\textwidth]{paper_automated/train_size_f1_micro.png}
        % \caption{}
        % \label{fig:train_size_micro}
    \end{subfigure}
    \begin{subfigure}[b]{0.6\textheight}
        \centering
        \includegraphics[width=\textwidth]{paper_automated/train_size_f1_macro.png}
        % \caption{}
        % \label{fig:train_size_macro}
    \end{subfigure}
    \caption[The relationship between the number of training examples and F1 score on MIMIC-IV \textit{ICD-9}]{The relationship between the number of training examples and F1 score on MIMIC-IV \textit{ICD-9}. The left figure shows the F1 Micro score on the y-axis, while the right figure shows the F1 Macro score.}
    \label{fig:train_size}
\end{figure}

### 2023-09-29 chapters/paper_benchmarking.tex
Write introduction, revise title and some formatting
Move table captions to top
Updates

\subsection{Variational recurrent neural network ({\small VRNN})}
The VRNN \cite{chung_recurrent_2015} is essentially a VAE per timestep. At timestep $t$, the VAE is conditioned on the hidden state of a recurrent neural network (RNN), $\db_{t}\in\mathbb{R}^{D_d}$, with state transition $\db_{t} = f([\xb_{t-1}, \zb_{t-1}], \db_{t-1})$ where $[\cdot, \cdot]$ denotes concatenation. 
The VRNN uses a Gated Recurrent Unit (GRU, \textcite{cho_properties_2014}) for $f$.
The joint distribution factorizes over time and the latent variables are autoregressive in both the observed and latent space,
\begin{equation}
    p(\xb_{1:T},\zb_{1:T}) = \prod_{t=1}^{T} p(\xb_t|\xb_{<t},\zb_{\leq t}) p(\zb_t|\xb_{<t},\zb_{<t}) \enspace . \label{eq: vrnn joint factorization}
\end{equation}
The approximate posterior similarly factorizes over time,
\begin{equation}
    q(\zb_{1:T}|\xb_{1:T}) = \prod_{t=1}^{T} q(\zb_t|\xb_{\leq t},\zb_{<t}) \enspace . \label{eq: vrnn inference factorization}
\end{equation}
From this, the ELBO for the VRNN is
\begin{equation}
    \mathcal{L}(\xb) = ~ \mathbb{E}_{q(\zb_{1:T}|\xb_{1:T})} \bigg[ \sum_{t} \log p(\xb_t|\xb_{<t},\zb_{\leq t}) - D_\text{KL}\left( q(\zb_t|\xb_{\leq t},\zb_{<t}) \, || \, p(\zb_t|\xb_{<t},\zb_{<t}) \right)  \bigg] \label{eq: vrnn elbo} \enspace .
\end{equation}
% \begin{equation}
% \begin{split}
%     \mathcal{L}(\xb) =&~ \mathbb{E}_{q(\zb_{1:T}|\xb_{1:T})} \bigg[ \sum_{t} \log p(\xb_t|\xb_{<t},\zb_{\leq t}) \\ & - \text{KL}\left( q(\zb_t|\xb_{\leq t},\zb_{<t}) \, || \, p(\zb_t|\xb_{<t},\zb_{<t}) \right)  \bigg] \enspace .
%     \label{eq: vrnn elbo}
% \end{split}
% \end{equation}
The VRNN uses diagonal covariance Gaussian distributions $\mathcal{N}$ for the prior and posterior distributions. We denote the output distribution of choice by $\mathcal{D}$. 
% \begin{align}
%     q(\zb_t|\xb_{\leq t},\zb_{<t}) &= \mathcal{N}\left(\alphab_{q}(\xb_{t},\db_{t})\right) \label{eq: vrnn parameterization inference} \\
%     p(\zb_t|\xb_{<t},\zb_{<t}) &= \mathcal{N}\left(\alphab_{p}(\db_t)\right) \label{eq: vrnn parameterization prior} \\
%     p(\xb_t|\xb_{<t},\zb_{\leq t}) &= \mathcal{D}\left(\betab(\zb_{t},\db_{t})\right) \enspace . \label{eq: vrnn parameterization observation}
% \end{align}
\begin{gather}
    p(\zb_t|\xb_{<t},\zb_{<t}) = \mathcal{N}\left(\alphab_{p}(\db_t)\right) \enspace , \nonumber \\
    p(\xb_t|\xb_{<t},\zb_{\leq t}) = \mathcal{D}\left(\betab(\zb_{t},\db_{t})\right) \enspace , \label{eq: vrnn parameterization generative} \\
    q(\zb_t|\xb_{\leq t},\zb_{<t}) = \mathcal{N}\left(\alphab_{q}(\xb_{t},\db_{t})\right) \enspace . \nonumber 
    \label{eq: vrnn parameterization inference}
\end{gather}
All sets of distributional parameters, $\alphab_q,\alphab_p$ and $\betab$, are the outputs of densely connected neural networks which we notationally overload as functions in equations~\cref{eq: vrnn parameterization generative} and \cref{eq: vrnn parameterization inference}. It is common to refer to $\alphab_q$ as the inference model or encoder and $\betab$ as the decoder. Together with $\betab$, the structural model $\alphab_p$ forms the generative model.

@@

@@

    \vspace{1mm}
    \caption{}
    \vspace{-1mm}

@@

    \caption[Model likelihoods and phoneme error rate for TIMIT.]{In \cref{tab: likelihoods timit} we report model likelihoods $\mathcal{L}$ for TIMIT represented as a 16bit $\mu$-law encoded PCM for different stochastic latent variable models and deterministic autoregressive baselines. 
    In \cref{tab: phoneme recognition (PER)} we report phoneme error rate (PER) of different representations for phoneme recognition on TIMIT. 

>>>>

\subsection{Variational recurrent neural network ({\small VRNN})}
The VRNN \cite{chung_recurrent_2015} is essentially a VAE per timestep. At timestep $t$, the VAE is conditioned on the hidden state of a recurrent neural network (RNN), $\db_{t}\in\mathbb{R}^{D_d}$, with state transition $\db_{t} = f([\xb_{t-1}, \zb_{t-1}], \db_{t-1})$ where $[\cdot, \cdot]$ denotes concatenation. 
The VRNN uses a Gated Recurrent Unit (GRU, \textcite{cho_properties_2014}) for $f$.
The joint distribution factorizes over time and the latent variables are autoregressive in both the observed and latent space,
\begin{equation}
    p(\xb_{1:T},\zb_{1:T}) = \prod_{t=1}^{T} p(\xb_t|\xb_{<t},\zb_{\leq t}) p(\zb_t|\xb_{<t},\zb_{<t}) \enspace . \label{eq: vrnn joint factorization}
\end{equation}
The approximate posterior similarly factorizes over time,
\begin{equation}
    q(\zb_{1:T}|\xb_{1:T}) = \prod_{t=1}^{T} q(\zb_t|\xb_{\leq t},\zb_{<t}) \enspace . \label{eq: vrnn inference factorization}
\end{equation}
From this, the ELBO for the VRNN is
\begin{equation}
    \mathcal{L}(\xb) = ~ \mathbb{E}_{q(\zb_{1:T}|\xb_{1:T})} \bigg[ \sum_{t} \log p(\xb_t|\xb_{<t},\zb_{\leq t}) - D_\text{KL}\left( q(\zb_t|\xb_{\leq t},\zb_{<t}) \parallel p(\zb_t|\xb_{<t},\zb_{<t}) \right)  \bigg] \label{eq: vrnn elbo} \enspace .
\end{equation}
% \begin{equation}
% \begin{split}
%     \mathcal{L}(\xb) =&~ \mathbb{E}_{q(\zb_{1:T}|\xb_{1:T})} \bigg[ \sum_{t} \log p(\xb_t|\xb_{<t},\zb_{\leq t}) \\ & - \text{KL}\left( q(\zb_t|\xb_{\leq t},\zb_{<t}) \parallel p(\zb_t|\xb_{<t},\zb_{<t}) \right)  \bigg] \enspace .
%     \label{eq: vrnn elbo}
% \end{split}
% \end{equation}
The VRNN uses diagonal covariance Gaussian distributions $\mathcal{N}$ for the prior and posterior distributions. We denote the output distribution of choice by $\mathcal{D}$. 
% \begin{align}
%     q(\zb_t|\xb_{\leq t},\zb_{<t}) &= \mathcal{N}\left(\alphab_{q}(\xb_{t},\db_{t})\right) \label{eq: vrnn parameterization inference} \\
%     p(\zb_t|\xb_{<t},\zb_{<t}) &= \mathcal{N}\left(\alphab_{p}(\db_t)\right) \label{eq: vrnn parameterization prior} \\
%     p(\xb_t|\xb_{<t},\zb_{\leq t}) &= \mathcal{D}\left(\betab(\zb_{t},\db_{t})\right) \enspace . \label{eq: vrnn parameterization observation}
% \end{align}
\begin{gather}
    p(\zb_t|\xb_{<t},\zb_{<t}) = \mathcal{N}\left(\alphab_{p}(\db_t)\right) \enspace , \nonumber \\
    p(\xb_t|\xb_{<t},\zb_{\leq t}) = \mathcal{D}\left(\betab(\zb_{t},\db_{t})\right) \enspace , \label{eq: vrnn parameterization generative} \\
    q(\zb_t|\xb_{\leq t},\zb_{<t}) = \mathcal{N}\left(\alphab_{q}(\xb_{t},\db_{t})\right) \enspace . \nonumber 
    \label{eq: vrnn parameterization inference}
\end{gather}
All sets of distributional parameters, $\alphab_q,\alphab_p$ and $\betab$, are the outputs of densely connected neural networks which we notationally overload as functions in equations~\cref{eq: vrnn parameterization generative} and \cref{eq: vrnn parameterization inference}. It is common to refer to $\alphab_q$ as the inference model or encoder and $\betab$ as the decoder. Together with $\betab$, the structural model $\alphab_p$ forms the generative model.

@@

    \caption[Model likelihoods and phoneme error rate for TIMIT.]{We report model likelihoods $\mathcal{L}$ for TIMIT represented as a 16bit $\mu$-law encoded PCM for different stochastic latent variable models and deterministic autoregressive baselines (left) and phoneme error rate (PER) of different representations for phoneme recognition on TIMIT (right).}

@@

    % \vspace{1mm}
    % \caption{}
    % \vspace{-1mm}

@@

### 2023-09-29 chapters/paper_retrospective.tex
Work on discussion and conclusion, plotting
Updates

The receiver operating characteristic (ROC) curve (\cref{fig_retrospective:figure1}, left) illustrates the potential to increase the sensitivity while maintaining a FPR lower than or equal to that of the call-takers. Similarly, the PPV sensitivity curve (\cref{fig_retrospective:figure1}, right) demonstrates that sensitivity can be improved while retaining a PPV higher than that of the call-takers. The framework can thus be tuned to a sensitivity of around 73\%, while still having a higher positive predictive value than the human call-taker (\cref{fig_retrospective:figure1}, right) The ensemble model outperformed the individual models regardless of the threshold, except for one that exhibited a slightly better sensitivity at a high FPR exceeding 1.5\%. The confusion matrices (\cref{fig_retrospective:figure2}) illustrate the performance differences in absolute numbers, with the model exhibiting more true positives and fewer false positives than the call-takers.

\begin{table}[t]
    \centering
    \caption[Overall stroke recognition performance of model compared to call takers.]{Overall performance on MH-1813 test data, performance without 1-1-2 training data, and performance on data from 2021 without diagnostic categories as well as performance on MH-1813 based on demographic subgroups (age/sex) [mean (95\% CI)].}
    \label{tab_retrospective:table2-main-results}
    \resizebox*{0.98\textwidth}{!}{%
    \begin{tabular}{l|ccccc}
        \toprule
                    & F1-score [\%] $\uparrow$ & Sensitivity [\%] $\uparrow$ & PPV [\%] $\uparrow$ & \makecell{FOR [\%] $\downarrow$ \\ (1 - specificity)} & \makecell{FPR [\%] $\downarrow$ \\ (1 - NPV)} \\

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\textwidth]{paper_retrospective/figure1.pdf}
    \caption[Receiver operator characteristic (ROC) curve and PPV-sensitivity curve for stroke recognition.]{Receiver operator characteristic (ROC) curve and PPV-sensitivity curve. Left, the ROC curve and, right, PPV-sensitivity curve (precision-recall curve). Models 1-5 are the individual models that make up the ensemble model.}
    \label{fig_retrospective:figure1}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\textwidth]{paper_retrospective/figure2.pdf}
    \caption[Prediction confusion matrices for stroke recognition.]{Prediction confusion matrices. Confusion matrices of predictions for call takers and the model on the test set. Numbers for the model are given as the rounded mean over eleven runs.}
    \label{fig_retrospective:figure2}
\end{figure}

@@

We performed an occlusion analysis to evaluate the importance of individual words for both positive and negative classifier predictions \cref{tab_retrospective:table3}
Among the words with a positive rank score, several words are synonymous with stroke, such as ``blood clot", ``haemorrhagic stroke", and ``stroke". Ambulances are rarely dispatched because the MH-1813 is not intended for emergencies. Therefore, a word like ``ambulance" may also be a strong indicator of call-taker recognition, which the model has learned to mimic. Additionally, most of the remaining words can be linked to stroke-related symptoms such as ``double vision", ``difficulties speaking", and ``hangs". Particularly, words describing the side of the body where symptoms occur ranked high (such as ``left", ``right", and ``side"). Finally, some words were also related to the sudden onset of symptoms (including ``suddenly" and ``minutes").

@@

\begin{table}[t]
    \centering
    \caption[Words with the largest positive and negative ranking score in calls predicted as stroke and non-stroke, respectively.]{English translation of words with the largest positive and negative ranking score in calls predicted as stroke and non-stroke, respectively.}
    \label{tab_retrospective:table3}
    \resizebox*{0.98\textwidth}{!}{%
    \begin{tabular}{l|lr|lr}
        \toprule
                    & \multicolumn{2}{c|}{Positive ranking score} & \multicolumn{2}{c}{Negative ranking score} \\
        \midrule
                    & \multicolumn{2}{c|}{Stroke predictions, $D=1,897$} & \multicolumn{2}{c}{Non-stroke predictions, $D=342,133$} \\
        \midrule
                    & Word, $w$ \textit{(translated)} & Occurences, $D^{(w)}$ & Word, $w$ \textit{(translated)} & Occurences, $D^{(w)}$ \\
        \midrule
        1.  & Ambulance & 1,680 & Tetanus & 4,378 \\        
        2.  & Blood clot & 895 & Pregnant & 8,749 \\        
        3.  & Left & 1,108 & Cut & 7,592 \\        
        4.  & Right & 1,050 & Bandage & 4,561 \\        
        5.  & Double vision & 84 & Amager (a location) & 23,776 \\        
        6.  & The words & 344 & O'clock & 94,436 \\        
        7.  & Suddenly & 783 & The emergency room & 42,809 \\        
        8.  & Arm & 709 & The police & 2,903 \\        
        9.  & Side & 1,139 & Swollen & 60,559 \\        
        10. & Stroke & 117 & Over the counter (OTC) & 4,641 \\        
        11. & Double & 113 & The neck & 30,151 \\        
        12. & Control & 134 & Fever & 112,586 \\        
        13. & Call & 39 & Prescription & 5,450 \\        
        14. & Numb & 94 & Centimetre & 12,026 \\        
        15. & Minutes & 763 & The knee & 8,875 \\        
        16. & Difficulties speaking & 44 & The pharmacy & 10,085 \\        
        17. & Haemorrhagic stroke & 133 & The stomach & 42,105 \\        
        18. & Hand & 297 & Psychiatric & 3,688 \\        
        19. & The ambulance & 521 & Pneumonia & 7,597 \\        
        20. & Slurred speech & 58 & Stomach pain & 10,551 \\        
        21. & Blood clots & 224 & Stool & 19,155 \\        
        22. & Fast & 663 & The ribs & 3,928 \\        
        23. & Express & 44 & Bleed & 10,501 \\        
        24. & Blood thinner & 259 & Bleeding & 24,313 \\        
        25. & Incoherent & 15 & Ribs & 2,941 \\        
        26. & Lopsided & 211 & Broken & 19,415 \\        
        27. & Reduced & 528 & Inflammation & 10,050 \\        
        28. & Hangs & 628 & Common cold & 8,127 \\        
        29. & Transient & 48 & Morning or morrow & 78,558 \\        
        30. & Not making sense & 14 & Swelling & 17,762 \\        
        \bottomrule
    \end{tabular}%
    }
\end{table}

@@

\subsubsection{Copenhagen Emergency Medical Services (CEMS)}

@@

\subsubsection{Danish Stroke Registry (DanStroke)}

@@

\subsubsection{Inclusion and ethics}

@@

\subsubsection{Cross-referencing data sources}

@@

\subsubsection{Dataset splitting}

@@

\subsubsection{Speech recognition}

@@

\subsubsection{Text classification}

@@

\subsubsection{Threshold calibration and ensembling}

@@

\subsubsection{Model training}

>>>>

The receiver operating characteristic (ROC) curve (\cref{fig_retrospective:figure1-roc-curve}, left) illustrates the potential to increase the sensitivity while maintaining a FPR lower than or equal to that of the call-takers. Similarly, the PPV sensitivity curve (\cref{fig_retrospective:figure1-roc-curve}, right) demonstrates that sensitivity can be improved while retaining a PPV higher than that of the call-takers. The framework can thus be tuned to a sensitivity of around 73\%, while still having a higher positive predictive value than the human call-taker (\cref{fig_retrospective:figure1-roc-curve}, right) The ensemble model outperformed the individual models regardless of the threshold, except for one that exhibited a slightly better sensitivity at a high FPR exceeding 1.5\%. The confusion matrices (\cref{fig_retrospective:figure2-prediction-confusion-matrices}) illustrate the performance differences in absolute numbers, with the model exhibiting more true positives and fewer false positives than the call-takers.

\begin{table}[t]
    \centering
    \caption[Overall stroke recognition performance of model compared to call takers.]{Overall performance on MH-1813 test data, performance without 1-1-2 training data, and performance on data from 2021 without diagnostic categories as well as performance on MH-1813 test data based on demographic subgroups (age/sex) [mean (95\% CI)].}
    \label{tab_retrospective:table2-main-results}
    \resizebox*{0.98\textwidth}{!}{%
    \begin{tabular}{l|ccccc}
        \toprule
                    & F1-score [\%] $\uparrow$ & Sensitivity [\%] $\uparrow$ & PPV [\%] $\uparrow$ & \makecell{FOR [\%] $\downarrow$ \\ (1 - specificity)} & \makecell{FPR [\%] $\downarrow$ \\ (1 - NPV)} \\

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\textwidth]{paper_retrospective/figure1.pdf}
    \caption[Receiver operator characteristic (ROC) curve and PPV-sensitivity curve for stroke recognition.]{Receiver operator characteristic (ROC) curve and PPV-sensitivity curve. Left, the ROC curve and, right, PPV-sensitivity curve (precision-recall curve). Models 1-5 are the individual models that make up the ensemble model.}
    \label{fig_retrospective:figure1-roc-curve}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\textwidth]{paper_retrospective/figure2.pdf}
    \caption[Prediction confusion matrices for stroke recognition.]{Prediction confusion matrices. Confusion matrices of predictions for call takers and the model on the test set. Numbers for the model are given as the rounded mean over eleven runs.}
    \label{fig_retrospective:figure2-prediction-confusion-matrices}
\end{figure}

@@

We performed an occlusion analysis to evaluate the importance of individual words for both positive and negative classifier predictions \cref{tab_retrospective:table3-occlusion-analysis}
Among the words with a positive rank score, several words are synonymous with stroke, such as ``blood clot", ``haemorrhagic stroke", and ``stroke". Ambulances are rarely dispatched because the MH-1813 is not intended for emergencies. Therefore, a word like ``ambulance" may also be a strong indicator of call-taker recognition, which the model has learned to mimic. Additionally, most of the remaining words can be linked to stroke-related symptoms such as ``double vision", ``difficulties speaking", and ``hangs". Particularly, words describing the side of the body where symptoms occur ranked high (such as ``left", ``right", and ``side"). Finally, some words were also related to the sudden onset of symptoms (including ``suddenly" and ``minutes").

@@

\begin{table}[t]
    \centering
    \caption[Words with the largest positive and negative ranking score in calls predicted as stroke and non-stroke, respectively.]{English translation of words with the largest positive and negative ranking score in calls predicted as stroke and non-stroke, respectively.}
    \label{tab_retrospective:table3-occlusion-analysis}
    \resizebox*{0.98\textwidth}{!}{%
    \begin{tabular}{l|lr|lr}
        \toprule
                    & \multicolumn{2}{c|}{Positive ranking score} & \multicolumn{2}{c}{Negative ranking score} \\
        \midrule
                    & \multicolumn{2}{c|}{Stroke predictions, $D=1,897$} & \multicolumn{2}{c}{Non-stroke predictions, $D=342,133$} \\
        \midrule
                    & Word, $w$ \textit{(translated)} & Occurences, $D^{(w)}$ & Word, $w$ \textit{(translated)} & Occurences, $D^{(w)}$ \\
        \midrule
        1.  & Ambulance & 1,680 & Tetanus & 4,378 \\        
        2.  & Blood clot & 895 & Pregnant & 8,749 \\        
        3.  & Left & 1,108 & Cut & 7,592 \\        
        4.  & Right & 1,050 & Bandage & 4,561 \\        
        5.  & Double vision & 84 & Amager (a location) & 23,776 \\        
        6.  & The words & 344 & O'clock & 94,436 \\        
        7.  & Suddenly & 783 & The emergency room & 42,809 \\        
        8.  & Arm & 709 & The police & 2,903 \\        
        9.  & Side & 1,139 & Swollen & 60,559 \\        
        10. & Stroke & 117 & Over the counter (OTC) & 4,641 \\        
        11. & Double & 113 & The neck & 30,151 \\        
        12. & Control & 134 & Fever & 112,586 \\        
        13. & Call & 39 & Prescription & 5,450 \\        
        14. & Numb & 94 & Centimetre & 12,026 \\        
        15. & Minutes & 763 & The knee & 8,875 \\        
        16. & Difficulties speaking & 44 & The pharmacy & 10,085 \\        
        17. & Haemorrhagic stroke & 133 & The stomach & 42,105 \\        
        18. & Hand & 297 & Psychiatric & 3,688 \\        
        19. & The ambulance & 521 & Pneumonia & 7,597 \\        
        20. & Slurred speech & 58 & Stomach pain & 10,551 \\        
        21. & Blood clots & 224 & Stool & 19,155 \\        
        22. & Fast & 663 & The ribs & 3,928 \\        
        23. & Express & 44 & Bleed & 10,501 \\        
        24. & Blood thinner & 259 & Bleeding & 24,313 \\        
        25. & Incoherent & 15 & Ribs & 2,941 \\        
        26. & Lopsided & 211 & Broken & 19,415 \\        
        27. & Reduced & 528 & Inflammation & 10,050 \\        
        28. & Hangs & 628 & Common cold & 8,127 \\        
        29. & Transient & 48 & Morning or morrow & 78,558 \\        
        30. & Not making sense & 14 & Swelling & 17,762 \\        
        \bottomrule
    \end{tabular}%
    }
\end{table}

@@

\paragraph{Copenhagen Emergency Medical Services (CEMS)}

@@

\paragraph{Danish Stroke Registry (DanStroke)}

@@

\paragraph{Inclusion and ethics}

@@

\paragraph{Cross-referencing data sources}

@@

\paragraph{Dataset splitting}

@@

\paragraph{Speech recognition}

@@

\paragraph{Text classification}

@@

\paragraph{Threshold calibration and ensembling}

@@

\paragraph{Model training}
